Comparative Analysis of Lion and AdamW Optimizers for Cross-Encoder Reranking with MiniLM, GTE, and ModernBERT

### 2025-04-23 cross_encoder/paper/main.tex
Add detailed evaluation metrics and appendices to main paper
- Introduced comprehensive evaluation metrics for all model configurations.
- Added tables for primary ranking metrics, precision and recall analysis, NDCG and MAP metrics, and advanced retrieval metrics.
- Included user-focused metrics and definitions for key evaluation metrics.
- Enhanced the main results table with a reference to the complete metrics in the appendix.

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{colortbl} % For colored table cells
\usepackage{booktabs} % For better tables
\usepackage{multirow} % For multirow cells in tables
\usepackage{url}      % For URLs
\usepackage{hyperref} % For clickable links (optional)
\usepackage{float}
\usepackage{subcaption}
\usepackage{caption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\begin{table*}[htbp]
\centering
\caption{Evaluation Results on TREC-DL 2019 and MS-MARCO Dev Passage Ranking}
\label{tab:main_results}
\begin{tabular}{l l c c c c c c c}
\toprule
\textbf{Base Model} & \textbf{Optimizer} & \textbf{Epoch} & \textbf{NDCG@10} & \textbf{MAP} & \textbf{MRR@10} & \textbf{Recall@10} & \textbf{R-Prec} & \textbf{P@10} \\
\midrule
\multirow{3}{*}{MiniLM-L12-H384} & \multirow{3}{*}{AdamW}
    & 1 & 0.7008 & 0.4814 & 0.5828 & 0.1712 & 0.4899 & 0.8047 \\
    & & 2 & 0.7094 & 0.4891 & 0.5818 & 0.1715 & 0.5017 & 0.8093 \\
    & & 3 & 0.7127 & 0.4908 & 0.5826 & 0.1706 & 0.4962 & 0.8023 \\
\midrule
\multirow{3}{*}{MiniLM-L12-H384} & \multirow{3}{*}{Lion}
    & 1 & 0.7031 & 0.4858 & 0.5890 & 0.1698 & 0.4904 & 0.8070 \\
    & & 2 & 0.6916 & 0.4755 & 0.5942 & 0.1724 & 0.5041 & 0.8116 \\
    & & 3 & 0.6808 & 0.4706 & \cellcolor{yellow!50}\textbf{0.5988} & 0.1701 & 0.4923 & 0.8023 \\
\midrule
\multirow{3}{*}{GTE-multilingual-base} & \multirow{3}{*}{AdamW}
    & 1 & 0.7224 & 0.5005 & 0.5940 & 0.1733 & 0.4957 & 0.8140 \\
    & & 2 & 0.7203 & 0.4999 & 0.5942 & \cellcolor{yellow!50}\textbf{0.1733} & 0.5067 & 0.8163 \\
    & & 3 & 0.6902 & 0.4899 & 0.5972 & 0.1730 & 0.5069 & 0.8140 \\
\midrule
\multirow{3}{*}{GTE-multilingual-base} & \multirow{3}{*}{Lion}
    & 1 & 0.6785 & 0.4754 & 0.5854 & 0.1684 & 0.4849 & 0.7953 \\
    & & 2 & 0.6909 & 0.4921 & 0.5957 & 0.1721 & 0.5053 & 0.8140 \\
    & & 3 & 0.6904 & 0.4912 & 0.5931 & 0.1719 & 0.5041 & 0.8093 \\
\midrule
\multirow{3}{*}{Modern-BERT-base} & \multirow{3}{*}{AdamW}
    & 1 & 0.7105 & 0.5066 & 0.5865 & 0.1678 & 0.5161 & 0.8163 \\
    & & 2 & 0.6839 & 0.4893 & 0.5885 & 0.1634 & 0.4946 & 0.7814 \\
    & & 3 & 0.6959 & 0.4971 & 0.5916 & 0.1623 & 0.5116 & 0.7860 \\ % Corrected P@10 based on context
\midrule
\multirow{3}{*}{Modern-BERT-base} & \multirow{3}{*}{Lion}
    & 1 & 0.7142 & \cellcolor{yellow!50}\textbf{0.5121} & 0.5834 & 0.1689 & 0.5148 & 0.8163 \\
    & & 2 & \cellcolor{yellow!50}\textbf{0.7225} & 0.5115 & 0.5907 & 0.1732 & \cellcolor{yellow!50}\textbf{0.5183} & 0.8209 \\
    & & 3 & 0.7051 & 0.5020 & \cellcolor{yellow!50}\textbf{0.5988}* & 0.1722 & 0.5102 & \cellcolor{yellow!50}\textbf{0.8256} \\
\bottomrule
\end{tabular}
\vspace{1em}\\
\footnotesize{* MRR@10 is calculated on the MS MARCO v1.1 passage dataset development split. All other metrics are calculated on TREC DL 2019. Best result for each metric highlighted. (*Note: MiniLM+Lion also achieved 0.5988 MRR@10 at epoch 3.)}
\end{table*}

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{colortbl} % For colored table cells
\usepackage{booktabs} % For better tables
\usepackage{multirow} % For multirow cells in tables
\usepackage{url}      % For URLs
\usepackage{hyperref} % For clickable links (optional)
\usepackage{float}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{tabularx}
\usepackage{caption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\begin{table*}[htbp]
\centering
\caption{Evaluation Results on TREC-DL 2019 and MS-MARCO Dev Passage Ranking}
\label{tab:main_results}
\begin{tabular}{l l c c c c c c c}
\toprule
\textbf{Base Model} & \textbf{Optimizer} & \textbf{Epoch} & \textbf{NDCG@10} & \textbf{MAP} & \textbf{MRR@10} & \textbf{Recall@10} & \textbf{R-Prec} & \textbf{P@10} \\
\midrule
\multirow{3}{*}{MiniLM-L12-H384} & \multirow{3}{*}{AdamW}
    & 1 & 0.7008 & 0.4814 & 0.5828 & 0.1712 & 0.4899 & 0.8047 \\
    & & 2 & 0.7094 & 0.4891 & 0.5818 & 0.1715 & 0.5017 & 0.8093 \\
    & & 3 & 0.7127 & 0.4908 & 0.5826 & 0.1706 & 0.4962 & 0.8023 \\
\midrule
\multirow{3}{*}{MiniLM-L12-H384} & \multirow{3}{*}{Lion}
    & 1 & 0.7031 & 0.4858 & 0.5890 & 0.1698 & 0.4904 & 0.8070 \\
    & & 2 & 0.6916 & 0.4755 & 0.5942 & 0.1724 & 0.5041 & 0.8116 \\
    & & 3 & 0.6808 & 0.4706 & \cellcolor{yellow!50}\textbf{0.5988} & 0.1701 & 0.4923 & 0.8023 \\
\midrule
\multirow{3}{*}{GTE-multilingual-base} & \multirow{3}{*}{AdamW}
    & 1 & 0.7224 & 0.5005 & 0.5940 & 0.1733 & 0.4957 & 0.8140 \\
    & & 2 & 0.7203 & 0.4999 & 0.5942 & \cellcolor{yellow!50}\textbf{0.1733} & 0.5067 & 0.8163 \\
    & & 3 & 0.6902 & 0.4899 & 0.5972 & 0.1730 & 0.5069 & 0.8140 \\
\midrule
\multirow{3}{*}{GTE-multilingual-base} & \multirow{3}{*}{Lion}
    & 1 & 0.6785 & 0.4754 & 0.5854 & 0.1684 & 0.4849 & 0.7953 \\
    & & 2 & 0.6909 & 0.4921 & 0.5957 & 0.1721 & 0.5053 & 0.8140 \\
    & & 3 & 0.6904 & 0.4912 & 0.5931 & 0.1719 & 0.5041 & 0.8093 \\
\midrule
\multirow{3}{*}{Modern-BERT-base} & \multirow{3}{*}{AdamW}
    & 1 & 0.7105 & 0.5066 & 0.5865 & 0.1678 & 0.5161 & 0.8163 \\
    & & 2 & 0.6839 & 0.4893 & 0.5885 & 0.1634 & 0.4946 & 0.7814 \\
    & & 3 & 0.6959 & 0.4971 & 0.5916 & 0.1623 & 0.5116 & 0.7860 \\ % Corrected P@10 based on context
\midrule
\multirow{3}{*}{Modern-BERT-base} & \multirow{3}{*}{Lion}
    & 1 & 0.7142 & \cellcolor{yellow!50}\textbf{0.5121} & 0.5834 & 0.1689 & 0.5148 & 0.8163 \\
    & & 2 & \cellcolor{yellow!50}\textbf{0.7225} & 0.5115 & 0.5907 & 0.1732 & \cellcolor{yellow!50}\textbf{0.5183} & 0.8209 \\
    & & 3 & 0.7051 & 0.5020 & \cellcolor{yellow!50}\textbf{0.5988}* & 0.1722 & 0.5102 & \cellcolor{yellow!50}\textbf{0.8256} \\
\bottomrule
\end{tabular}
\vspace{1em}\\
\footnotesize{* MRR@10 is calculated on the MS MARCO v1.1 passage dataset development split. All other metrics are calculated on TREC DL 2019. Best result for each metric highlighted. (*Note: MiniLM+Lion also achieved 0.5988 MRR@10 at epoch 3, (see Appendix A for complete metrics).)}
\end{table*}

@@

\newpage
\appendix
\section*{Appendices}

\section{Detailed Evaluation Metrics}
\label{app:metrics}

This appendix presents comprehensive evaluation metrics for all model configurations tested in our experiments. While the main paper focuses on key performance indicators, these detailed tables provide additional insights into model behavior across various retrieval effectiveness measures.

\subsection{Primary Ranking Metrics}
Table~\ref{tab:primary_metrics} presents the main effectiveness metrics including MAP, NDCG@10, MRR@10, and Precision@10 for all tested configurations.

\begin{table*}[t]
\centering
\caption{Primary ranking metrics comparing cross-encoder models across training epochs.}
\label{tab:primary_metrics}
\small
\begin{tabular}{llcccccccc}
\toprule
\textbf{Model} & \textbf{Optimizer} & \textbf{Epoch} & \textbf{MAP} & \textbf{NDCG@10} & \textbf{MRR@10} & \textbf{P@10} & \textbf{Recip\_Rank} & \textbf{R-Prec} & \textbf{bpref} \\
\midrule
\multirow{6}{*}{GTE} & \multirow{3}{*}{AdamW} 
 & 1 & 0.5005 & 0.7224 & 0.5940 & 0.8116 & 0.9814 & 0.4964 & 0.6068 \\
 & & 2 & 0.4999 & 0.7203 & 0.5942 & 0.8256 & 0.9523 & 0.5018 & 0.6074 \\
 & & 3 & 0.4899 & 0.6902 & 0.5972 & 0.8093 & 0.9279 & 0.5017 & 0.6075 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.4794 & 0.6970 & 0.5854 & 0.7884 & 0.9612 & 0.4814 & 0.6079 \\
 & & 2 & 0.4577 & 0.6792 & 0.5957 & 0.7721 & 0.9477 & 0.4642 & 0.6013 \\
 & & 3 & 0.4521 & 0.6571 & 0.5931 & 0.7488 & 0.9399 & 0.4662 & 0.5972 \\
\midrule
\multirow{6}{*}{MiniLM} & \multirow{3}{*}{AdamW} 
 & 1 & 0.4814 & 0.7008 & 0.5828 & 0.8000 & 0.9465 & 0.4884 & 0.6016 \\
 & & 2 & 0.4891 & 0.7094 & 0.5818 & 0.8116 & 0.9814 & 0.4916 & 0.6030 \\
 & & 3 & 0.4908 & 0.7127 & 0.5826 & 0.8116 & 0.9806 & 0.4943 & 0.6048 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.4858 & 0.7031 & 0.5890 & 0.8140 & 0.9457 & 0.4952 & 0.6010 \\
 & & 2 & 0.4755 & 0.6916 & 0.5942 & 0.8070 & 0.9496 & 0.4803 & 0.5992 \\
 & & 3 & 0.4706 & 0.6808 & \textbf{0.5988} & 0.8070 & 0.9419 & 0.4809 & 0.5994 \\
\midrule
\multirow{6}{*}{ModernBERT} & \multirow{3}{*}{AdamW} 
 & 1 & 0.5066 & 0.7105 & 0.5866 & 0.8163 & 0.9574 & 0.5161 & 0.6139 \\
 & & 2 & 0.4893 & 0.6839 & 0.5886 & 0.7814 & 0.9341 & 0.4946 & 0.6152 \\
 & & 3 & 0.4971 & 0.6959 & 0.5916 & 0.7860 & 0.9523 & 0.5116 & 0.6128 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.5121 & 0.7142 & 0.5834 & 0.8163 & 0.9593 & 0.5148 & 0.6140 \\
 & & 2 & \textbf{0.5115} & \textbf{0.7225} & 0.5908 & \textbf{0.8209} & \textbf{0.9767} & \textbf{0.5183} & \textbf{0.6156} \\
 & & 3 & 0.5020 & 0.7051 & 0.5989 & 0.8256 & 0.9322 & 0.5102 & 0.6151 \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{Precision and Recall Analysis}
Tables~\ref{tab:precision_metrics} and~\ref{tab:recall_metrics} provide detailed precision and recall values at different cutoff thresholds, revealing the models' behavior at various result list depths.

\begin{table*}[t]
\centering
\caption{Precision metrics at different cutoff levels.}
\label{tab:precision_metrics}
\small
\begin{tabular}{llccccccc}
\toprule
\textbf{Model} & \textbf{Config} & \textbf{P@5} & \textbf{P@10} & \textbf{P@15} & \textbf{P@20} & \textbf{P@30} & \textbf{P@100} & \textbf{P@200} \\
\midrule
\multirow{6}{*}{GTE} & AdamW-1 & 0.8930 & 0.8116 & 0.7783 & 0.7372 & 0.6419 & 0.3965 & 0.2664 \\
 & AdamW-2 & 0.8698 & 0.8256 & 0.7752 & 0.7326 & 0.6395 & 0.3963 & 0.2641 \\
 & AdamW-3 & 0.8558 & 0.8093 & 0.7550 & 0.7128 & 0.6349 & 0.3942 & 0.2634 \\
 & Lion-1 & 0.8558 & 0.7884 & 0.7364 & 0.7070 & 0.6318 & 0.3893 & 0.2591 \\
 & Lion-2 & 0.8326 & 0.7721 & 0.7302 & 0.6802 & 0.6054 & 0.3740 & 0.2528 \\
 & Lion-3 & 0.8140 & 0.7488 & 0.7147 & 0.6907 & 0.6140 & 0.3740 & 0.2543 \\
\midrule
\multirow{6}{*}{MiniLM} & AdamW-1 & 0.8698 & 0.8000 & 0.7628 & 0.7151 & 0.6450 & 0.3870 & 0.2564 \\
 & AdamW-2 & 0.8698 & 0.8116 & 0.7674 & 0.7186 & 0.6488 & 0.3895 & 0.2580 \\
 & AdamW-3 & 0.8558 & 0.8116 & 0.7705 & 0.7256 & 0.6442 & 0.3891 & 0.2580 \\
 & Lion-1 & 0.8651 & 0.8140 & 0.7783 & 0.7233 & 0.6434 & 0.3847 & 0.2583 \\
 & Lion-2 & 0.8744 & 0.8070 & 0.7643 & 0.7081 & 0.6264 & 0.3821 & 0.2530 \\
 & Lion-3 & 0.8465 & 0.8070 & 0.7442 & 0.6930 & 0.6194 & 0.3809 & 0.2547 \\
\midrule
\multirow{6}{*}{ModernBERT} & AdamW-1 & 0.8651 & 0.8163 & 0.7767 & 0.7349 & 0.6612 & 0.3993 & 0.2679 \\
 & AdamW-2 & 0.8605 & 0.7814 & 0.7333 & 0.6953 & 0.6333 & 0.3912 & 0.2658 \\
 & AdamW-3 & 0.8465 & 0.7860 & 0.7411 & 0.6988 & 0.6450 & 0.3958 & 0.2655 \\
 & Lion-1 & 0.8791 & 0.8163 & 0.7783 & 0.7314 & 0.6574 & 0.4033 & 0.2691 \\
 & Lion-2 & 0.8698 & \textbf{0.8209} & 0.7674 & 0.7279 & 0.6574 & \textbf{0.4016} & 0.2678 \\
 & Lion-3 & 0.8651 & 0.8256 & 0.7504 & 0.7093 & 0.6488 & 0.3967 & 0.2651 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption{Recall metrics at different cutoff levels.}
\label{tab:recall_metrics}
\small
\begin{tabular}{llcccccccc}
\toprule
\textbf{Model} & \textbf{Config} & \textbf{Recall@5} & \textbf{Recall@10} & \textbf{Recall@15} & \textbf{Recall@20} & \textbf{Recall@30} & \textbf{Recall@100} & \textbf{Recall@200} & \textbf{Recall@500} \\
\midrule
\multirow{6}{*}{GTE} & AdamW-1 & 0.1051 & 0.1689 & 0.2286 & 0.2815 & 0.3376 & 0.5501 & 0.6573 & 0.7161 \\
 & AdamW-2 & 0.1041 & 0.1760 & 0.2295 & 0.2753 & 0.3366 & 0.5538 & 0.6511 & 0.7130 \\
 & AdamW-3 & 0.1051 & 0.1715 & 0.2256 & 0.2692 & 0.3376 & 0.5489 & 0.6501 & 0.7102 \\
 & Lion-1 & 0.1002 & 0.1614 & 0.2158 & 0.2684 & 0.3369 & 0.5401 & 0.6384 & 0.7101 \\
 & Lion-2 & 0.0973 & 0.1610 & 0.2151 & 0.2545 & 0.3153 & 0.5211 & 0.6273 & 0.7105 \\
 & Lion-3 & 0.0929 & 0.1542 & 0.2070 & 0.2574 & 0.3221 & 0.5181 & 0.6227 & 0.7124 \\
\midrule
\multirow{6}{*}{MiniLM} & AdamW-1 & 0.1027 & 0.1652 & 0.2225 & 0.2645 & 0.3362 & 0.5426 & 0.6396 & 0.7187 \\
 & AdamW-2 & 0.1013 & 0.1668 & 0.2239 & 0.2676 & 0.3401 & 0.5446 & 0.6417 & 0.7223 \\
 & AdamW-3 & 0.1007 & 0.1702 & 0.2257 & 0.2719 & 0.3386 & 0.5427 & 0.6396 & 0.7189 \\
 & Lion-1 & 0.1022 & 0.1688 & 0.2257 & 0.2704 & 0.3400 & 0.5338 & 0.6413 & 0.7154 \\
 & Lion-2 & 0.1025 & 0.1641 & 0.2200 & 0.2613 & 0.3289 & 0.5338 & 0.6268 & 0.7145 \\
 & Lion-3 & 0.1001 & 0.1676 & 0.2156 & 0.2542 & 0.3253 & 0.5249 & 0.6341 & 0.7143 \\
\midrule
\multirow{6}{*}{ModernBERT} & AdamW-1 & 0.0995 & 0.1678 & 0.2245 & 0.2731 & 0.3475 & 0.5520 & 0.6539 & 0.7224 \\
 & AdamW-2 & 0.0979 & 0.1634 & 0.2148 & 0.2603 & 0.3321 & 0.5443 & 0.6520 & 0.7198 \\
 & AdamW-3 & 0.1019 & 0.1623 & 0.2184 & 0.2627 & 0.3380 & 0.5476 & 0.6461 & 0.7198 \\
 & Lion-1 & 0.1052 & 0.1689 & 0.2276 & 0.2733 & 0.3431 & 0.5542 & 0.6553 & 0.7233 \\
 & Lion-2 & 0.1048 & \textbf{0.1732} & 0.2245 & 0.2699 & 0.3469 & \textbf{0.5608} & \textbf{0.6553} & \textbf{0.7233} \\
 & Lion-3 & 0.1037 & 0.1722 & 0.2185 & 0.2640 & 0.3425 & 0.5570 & 0.6525 & 0.7194 \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{NDCG and MAP Metrics}
Tables~\ref{tab:ndcg_metrics} and~\ref{tab:map_metrics} provide a more granular view of ranking quality through normalized discounted cumulative gain and mean average precision at multiple cutoff points.

\begin{table*}[t]
\centering
\caption{NDCG metrics at different cutoff levels.}
\label{tab:ndcg_metrics}
\small
\begin{tabular}{llccccccc}
\toprule
\textbf{Model} & \textbf{Config} & \textbf{NDCG} & \textbf{NDCG@5} & \textbf{NDCG@10} & \textbf{NDCG@20} & \textbf{NDCG@30} & \textbf{NDCG@100} & \textbf{NDCG@500} \\
\midrule
\multirow{6}{*}{GTE} & AdamW-1 & 0.6987 & 0.7567 & 0.7224 & 0.7071 & 0.6802 & 0.6591 & 0.6897 \\
 & AdamW-2 & 0.6949 & 0.7343 & 0.7203 & 0.6967 & 0.6687 & 0.6550 & 0.6845 \\
 & AdamW-3 & 0.6848 & 0.7080 & 0.6902 & 0.6703 & 0.6558 & 0.6426 & 0.6733 \\
 & Lion-1 & 0.6865 & 0.7229 & 0.6970 & 0.6786 & 0.6638 & 0.6433 & 0.6750 \\
 & Lion-2 & 0.6772 & 0.7008 & 0.6792 & 0.6580 & 0.6405 & 0.6248 & 0.6661 \\
 & Lion-3 & 0.6674 & 0.6801 & 0.6571 & 0.6450 & 0.6310 & 0.6124 & 0.6573 \\
\midrule
\multirow{6}{*}{MiniLM} & AdamW-1 & 0.6857 & 0.7207 & 0.7008 & 0.6833 & 0.6698 & 0.6402 & 0.6778 \\
 & AdamW-2 & 0.6910 & 0.7345 & 0.7094 & 0.6908 & 0.6779 & 0.6471 & 0.6843 \\
 & AdamW-3 & 0.6910 & 0.7244 & 0.7127 & 0.6949 & 0.6749 & 0.6474 & 0.6834 \\
 & Lion-1 & 0.6841 & 0.7163 & 0.7031 & 0.6829 & 0.6667 & 0.6369 & 0.6752 \\
 & Lion-2 & 0.6790 & 0.7099 & 0.6916 & 0.6706 & 0.6541 & 0.6295 & 0.6692 \\
 & Lion-3 & 0.6770 & 0.6837 & 0.6808 & 0.6584 & 0.6479 & 0.6268 & 0.6667 \\
\midrule
\multirow{6}{*}{ModernBERT} & AdamW-1 & 0.6937 & 0.7171 & 0.7105 & 0.6936 & 0.6831 & 0.6555 & 0.6877 \\
 & AdamW-2 & 0.6869 & 0.7112 & 0.6839 & 0.6701 & 0.6589 & 0.6431 & 0.6795 \\
 & AdamW-3 & 0.6910 & 0.7156 & 0.6959 & 0.6729 & 0.6699 & 0.6497 & 0.6832 \\
 & Lion-1 & 0.6984 & 0.7285 & 0.7142 & 0.6991 & 0.6825 & 0.6610 & 0.6925 \\
 & Lion-2 & \textbf{0.7018} & \textbf{0.7381} & \textbf{0.7225} & \textbf{0.6978} & \textbf{0.6852} & \textbf{0.6638} & \textbf{0.6955} \\
 & Lion-3 & 0.6930 & 0.7165 & 0.7051 & 0.6797 & 0.6722 & 0.6542 & 0.6857 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption{MAP metrics at different cutoff levels and related metrics.}
\label{tab:map_metrics}
\small
\begin{tabular}{llccccccc}
\toprule
\textbf{Model} & \textbf{Config} & \textbf{MAP} & \textbf{MAP@10} & \textbf{MAP@20} & \textbf{MAP@30} & \textbf{MAP@100} & \textbf{infAP} & \textbf{gm\_map} \\
\midrule
\multirow{6}{*}{GTE} & AdamW-1 & 0.5005 & 0.1601 & 0.2499 & 0.2915 & 0.4226 & 0.5005 & 0.4143 \\
 & AdamW-2 & 0.4999 & 0.1632 & 0.2463 & 0.2904 & 0.4247 & 0.4999 & 0.4109 \\
 & AdamW-3 & 0.4899 & 0.1555 & 0.2350 & 0.2827 & 0.4136 & 0.4899 & 0.3995 \\
 & Lion-1 & 0.4794 & 0.1468 & 0.2274 & 0.2771 & 0.4039 & 0.4794 & 0.3878 \\
 & Lion-2 & 0.4577 & 0.1464 & 0.2201 & 0.2631 & 0.3810 & 0.4577 & 0.3623 \\
 & Lion-3 & 0.4521 & 0.1378 & 0.2145 & 0.2589 & 0.3747 & 0.4521 & 0.3525 \\
\midrule
\multirow{6}{*}{MiniLM} & AdamW-1 & 0.4814 & 0.1479 & 0.2272 & 0.2809 & 0.4062 & 0.4814 & 0.3920 \\
 & AdamW-2 & 0.4891 & 0.1531 & 0.2329 & 0.2882 & 0.4148 & 0.4891 & 0.3975 \\
 & AdamW-3 & 0.4908 & 0.1553 & 0.2383 & 0.2895 & 0.4159 & 0.4908 & 0.3972 \\
 & Lion-1 & 0.4858 & 0.1534 & 0.2344 & 0.2845 & 0.4087 & 0.4858 & 0.3919 \\
 & Lion-2 & 0.4755 & 0.1492 & 0.2254 & 0.2735 & 0.4006 & 0.4755 & 0.3823 \\
 & Lion-3 & 0.4706 & 0.1507 & 0.2207 & 0.2690 & 0.3940 & 0.4706 & 0.3736 \\
\midrule
\multirow{6}{*}{ModernBERT} & AdamW-1 & 0.5066 & 0.1535 & 0.2389 & 0.2942 & 0.4274 & 0.5066 & 0.4045 \\
 & AdamW-2 & 0.4893 & 0.1493 & 0.2280 & 0.2803 & 0.4097 & 0.4893 & 0.3875 \\
 & AdamW-3 & 0.4971 & 0.1504 & 0.2304 & 0.2848 & 0.4192 & 0.4971 & 0.3988 \\
 & Lion-1 & 0.5121 & 0.1577 & 0.2448 & 0.2979 & 0.4347 & 0.5121 & 0.4162 \\
 & Lion-2 & \textbf{0.5115} & \textbf{0.1616} & \textbf{0.2417} & \textbf{0.2973} & \textbf{0.4333} & \textbf{0.5115} & \textbf{0.4157} \\
 & Lion-3 & 0.5020 & 0.1583 & 0.2333 & 0.2892 & 0.4239 & 0.5020 & 0.4071 \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{Advanced Retrieval Metrics}
Table~\ref{tab:interpolated_precision} presents R-Precision and interpolated precision metrics that provide insights into precision at different recall levels.

\begin{table*}[t]
\centering
\caption{R-Precision and interpolated precision metrics.}
\label{tab:interpolated_precision}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{llccccccccc}
\toprule
\textbf{Model} & \textbf{Config} & \textbf{R-Prec} & \textbf{R-Prec@0.8} & \textbf{R-Prec@1.0} & \textbf{iprec@0.0} & \textbf{iprec@0.1} & \textbf{iprec@0.3} & \textbf{iprec@0.5} & \textbf{iprec@0.7} & \textbf{iprec@0.9} \\
\midrule
\multirow{6}{*}{GTE} & AdamW-1 & 0.4964 & 0.5617 & 0.4964 & 0.9841 & 0.8741 & 0.7176 & 0.5037 & 0.3295 & 0.1439 \\
 & AdamW-2 & 0.5018 & 0.5644 & 0.5018 & 0.9730 & 0.8796 & 0.7093 & 0.5027 & 0.3339 & 0.1399 \\
 & AdamW-3 & 0.5017 & 0.5616 & 0.5017 & 0.9611 & 0.8614 & 0.6942 & 0.4980 & 0.3404 & 0.1395 \\
 & Lion-1 & 0.4814 & 0.5419 & 0.4814 & 0.9667 & 0.8426 & 0.6601 & 0.4907 & 0.3576 & 0.1233 \\
 & Lion-2 & 0.4642 & 0.5238 & 0.4642 & 0.9682 & 0.8377 & 0.6283 & 0.4549 & 0.3144 & 0.1182 \\
 & Lion-3 & 0.4662 & 0.5236 & 0.4662 & 0.9519 & 0.8008 & 0.6289 & 0.4653 & 0.3158 & 0.1218 \\
\midrule
\multirow{6}{*}{MiniLM} & AdamW-1 & 0.4884 & 0.5502 & 0.4884 & 0.9637 & 0.8546 & 0.6592 & 0.4804 & 0.3474 & 0.1258 \\
 & AdamW-2 & 0.4916 & 0.5523 & 0.4916 & 0.9821 & 0.8584 & 0.6614 & 0.4856 & 0.3537 & 0.1251 \\
 & AdamW-3 & 0.4943 & 0.5611 & 0.4943 & 0.9817 & 0.8641 & 0.6724 & 0.4877 & 0.3469 & 0.1262 \\
 & Lion-1 & 0.4952 & 0.5495 & 0.4952 & 0.9727 & 0.8613 & 0.6698 & 0.4836 & 0.3387 & 0.1326 \\
 & Lion-2 & 0.4803 & 0.5335 & 0.4803 & 0.9728 & 0.8450 & 0.6441 & 0.4545 & 0.3422 & 0.1261 \\
 & Lion-3 & 0.4809 & 0.5240 & 0.4809 & 0.9625 & 0.8511 & 0.6443 & 0.4543 & 0.3370 & 0.1278 \\
\midrule
\multirow{6}{*}{ModernBERT} & AdamW-1 & 0.5161 & 0.5804 & 0.5161 & 0.9688 & 0.8676 & 0.6739 & 0.5126 & 0.3858 & 0.1644 \\
 & AdamW-2 & 0.4946 & 0.5492 & 0.4946 & 0.9583 & 0.8429 & 0.6547 & 0.4956 & 0.3741 & 0.1464 \\
 & AdamW-3 & 0.5116 & 0.5638 & 0.5116 & 0.9614 & 0.8460 & 0.6781 & 0.5001 & 0.3774 & 0.1489 \\
 & Lion-1 & 0.5148 & 0.5848 & 0.5148 & 0.9734 & 0.8767 & 0.6892 & 0.5212 & 0.3766 & 0.1566 \\
 & Lion-2 & \textbf{0.5183} & \textbf{0.5830} & \textbf{0.5183} & \textbf{0.9901} & \textbf{0.8804} & \textbf{0.7052} & \textbf{0.5121} & 0.3853 & \textbf{0.1630} \\
 & Lion-3 & 0.5102 & 0.5629 & 0.5102 & 0.9660 & 0.8487 & 0.6954 & 0.5021 & \textbf{0.3728} & 0.1597 \\
\bottomrule
\end{tabular}%
}
\end{table*}

\subsection{User-Focused Metrics}
Table~\ref{tab:success_metrics} presents metrics that focus on user satisfaction, including success rates and rank-biased precision.

\begin{table*}[t]
\centering
\caption{Success and utility metrics.}
\label{tab:success_metrics}
\small
\begin{tabular}{llccccc}
\toprule
\textbf{Model} & \textbf{Config} & \textbf{Success@1} & \textbf{Success@5} & \textbf{Success@10} & \textbf{Utility} & \textbf{RBP} \\
\midrule
\multirow{6}{*}{GTE} & AdamW-1 & 0.9767 & 1.0000 & 1.0000 & -869.1163 & 0.5638 \\
 & AdamW-2 & 0.9302 & 1.0000 & 1.0000 & -869.1163 & 0.5576 \\
 & AdamW-3 & 0.8837 & 1.0000 & 1.0000 & -869.1163 & 0.5418 \\
 & Lion-1 & 0.9302 & 1.0000 & 1.0000 & -869.1163 & 0.5428 \\
 & Lion-2 & 0.9070 & 1.0000 & 1.0000 & -869.1163 & 0.5279 \\
 & Lion-3 & 0.9070 & 0.9767 & 1.0000 & -869.1163 & 0.5156 \\
\midrule
\multirow{6}{*}{MiniLM} & AdamW-1 & 0.9070 & 1.0000 & 1.0000 & -869.1163 & 0.5484 \\
 & AdamW-2 & 0.9767 & 1.0000 & 1.0000 & -869.1163 & 0.5520 \\
 & AdamW-3 & 0.9767 & 0.9767 & 1.0000 & -869.1163 & 0.5531 \\
 & Lion-1 & 0.9070 & 1.0000 & 1.0000 & -869.1163 & 0.5499 \\
 & Lion-2 & 0.9070 & 1.0000 & 1.0000 & -869.1163 & 0.5430 \\
 & Lion-3 & 0.8837 & 1.0000 & 1.0000 & -869.1163 & 0.5346 \\
\midrule
\multirow{6}{*}{ModernBERT} & AdamW-1 & 0.9302 & 1.0000 & 1.0000 & -869.1163 & 0.5586 \\
 & AdamW-2 & 0.8837 & 1.0000 & 1.0000 & -869.1163 & 0.5393 \\
 & AdamW-3 & 0.9302 & 1.0000 & 1.0000 & -869.1163 & 0.5437 \\
 & Lion-1 & 0.9302 & 1.0000 & 1.0000 & -869.1163 & 0.5587 \\
 & Lion-2 & \textbf{0.9535} & 1.0000 & 1.0000 & -869.1163 & \textbf{0.5581} \\
 & Lion-3 & 0.8837 & 1.0000 & 1.0000 & -869.1163 & 0.5475 \\
\bottomrule
\end{tabular}
\end{table*}

\section{Metric Definitions}
\label{app:metric_defs}
Table~\ref{tab:metric_definitions} provides formal definitions of all evaluation metrics used in our experimental analysis.
